Real Time Shape Reconstruction for Near Earth Asteroid Landing

### 2018-04-01 abstract.tex
Working on abstract

The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
\begin{align}
    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
\end{align}
The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
\begin{align}
    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
\end{align}
This approach relates the uncertainty of the measurement with the distance to a given vertex.
As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
From Bayes' theorem, the a posterior probability is
\begin{align}
    p(\norm{\vb{v}_i} | \norm{\vb{p}_i}) = \frac{p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i})}{p(\norm{\vb{p}_i}} \propto p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i}).
\end{align}
From the properties of a Gaussian the a posterior probability is also distributed according to a Gaussian distribution
\begin{align}
    Gaussian
\end{align}

>>>>

The variance for each measurement vector is assumed to be related to the ``distance'' from the measurement to vertex \( \vb{v}_i \).
Here we use the geodesic distance to parameterize the difference, and hence  uncertainty, or associating the measurement with a given vertex.
From spherical trigonometry the central angle between measurement \( \vb{p}_i \) and vertex \( \vb{v}_i \) of the shape estimate is
\begin{align}
    \Delta \sigma_i = \arctan \parenth{\frac{\norm{\vb{p}_i \times \vb{v}_i}}{\vb{p}_i \cdot \vb{v}_i }}.
\end{align}
The variance of measurement \( \vb{p}_i \) with respect to vertex \( \vb{v}_i \) is then defined as the arc length as
\begin{align}
    w_{m, i} = \norm{\vb{p}_i} \Delta \sigma .
\end{align}
This approach relates the uncertainty of the measurement with the distance to a given vertex.
As a result, measurements which are far from a vertex, where \( \Delta \sigma \) is large, will tend to have a larger variance and hence uncertainty. 
From Bayes' theorem, the a posterior probability is
\begin{align}
    p(\norm{\vb{v}_i} | \norm{\vb{p}_i}) = \frac{p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i})}{p(\norm{\vb{p}_i}} \propto p(\norm{\vb{p}_i} | \norm{\vb{v}_i}) p(\norm{\vb{v}_i}).
\end{align}
From the properties of a Gaussian the a posterior probability given a measurement is also distributed according to a Gaussian distribution
\begin{align}
    \mathcal{N} \parenth{\frac{w_{m, i}^2 r_0 + w_0^2 r_{m, i}}{w_0^2 + w_{m, i}^2} , \frac{w_0^2 + w_{m, i}^2}{w_0^2 + w_{m, i}^2}} .
\end{align}
The a posterior probability conditioned on the measurement is the weighted average of the prior knowledge and the measurement. 
Measurements that are far from the vertex will have a high uncertainty or variance and will have a reduced impact on the vertex.
Additional measurements are incoporated using a weighted average of prior belief and the measurement uncertainty.

In order to improve the computational efficiency measurement updates are assumed to be local in nature.
Instead of applying a measurement to all vertices of the mesh the measurement is only applied to the vertices which are within a specified region of the measurement.
